### 2017-11-15 Draft2/Appending.Compare.tex
Remove undefined references

In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively. I derived earlier that
\begin{align*}
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncWritesDynamicArray(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
\end{align*}
From Theorem \ref{thm:BothSidesInequality} and Corollary \ref{coro:BothSidesNonStrictInequality}, I may divide all sides of this inequality by $n$ to receive
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} n &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}
It was shown earlier that $\FuncWritesGrowthArray(n) \sim n$. From Theorem \ref{thm:MergesOverOps}, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$. From Theorem \ref{thm:InterchangeableInInequality} and Corollary \ref{coro:InterchangeableInNonStrictInequality}, it follows that
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} {\FuncWritesGrowthArray(n)} &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}
\HdrSpaceComplexCmp

>>>>

In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively. I derived earlier that
\begin{align*}
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncWritesDynamicArray(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
\end{align*}
From Theorem \ref{thm:BothSidesInequality}, I may divide all sides of this inequality by $n$ to receive
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} n &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}
It was shown earlier that $\FuncWritesGrowthArray(n) \sim n$. From Theorem \ref{thm:MergesOverOps}, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$. From Theorem \ref{thm:InterchangeableInInequality}, it follows that
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} {\FuncWritesGrowthArray(n)} &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}
\HdrSpaceComplexCmp

### 2017-11-15 Draft2/Appending.Dynamic.tex
Add pictures, [WIP] title all the algos
Remove undefined references

\begin{algorithm}[H]
	\begin{algorithmic}[1]
		\Procedure{$\FuncAppend$}{$\VarList,\ \ParamItem$}
			\If{$\VarList.\FieldFull$}
				\State $\VarList.\FuncGrow()$
			\EndIf

@@

I can build on this inequality to receive asymptotic bounds for $\FuncWrites(n)$:
\begin{align*}
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequalityAdd}, Corollary \ref{coro:BothSidesNonStrictInequalityAdd})}
\end{align*}
\HdrSpaceComplex

@@

First, from the definition of $\VarList.\FieldCapacity$, note that a dynamic array's capacity is the length of the buffer it stores its items in. Then a buffer of length $c$ is allocated at some point if and only if $c \in \VarCapacitySeq$. Then the total length of those buffers is
\begin{align*}
\FuncSpace(n) &= \sum_i {\VarCapacitySeq_i}\\
&= \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^\VarUseful\VarInitCapacity\\
&= \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
\end{align*}
Using Lemma \ref{lem:ToVarUsefulPowerBounds} again, I asymptotically bound $\FuncSpace(n)$:
\begin{align*}
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}
\end{align*}

>>>>

\begin{algorithm}[H]
	\caption{Appending \TextDynamicArray}
	\begin{algorithmic}[1]
		\Procedure{$\FuncAppend$}{$\VarList,\ \ParamItem$}
			\If{$\VarList.\FieldFull$}
				\State $\VarList.\FuncGrow()$
			\EndIf

@@

I can build on this inequality to receive asymptotic bounds for $\FuncWrites(n)$:
\begin{align*}
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality})}\\
\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality})}\\
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequalityAdd})}
\end{align*}
\HdrSpaceComplex

@@

First, from the definition of $\VarList.\FieldCapacity$, note that a dynamic array's capacity is the length of the buffer it stores its items in. Then a buffer of length $c$ is allocated at some point if and only if $c \in \VarCapacitySeq$. Then the total length of those buffers is
\begin{align*}
\FuncSpace(n) &= \sum_i {\VarCapacitySeq_i}\\
&= \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^\VarUseful\VarInitCapacity\\
&= \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
\end{align*}
Using Lemma \ref{lem:ToVarUsefulPowerBounds} again, I asymptotically bound $\FuncSpace(n)$:
\begin{align*}
\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Theorem \ref{thm:BothSidesInequality})}\\
\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality})}\\
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequality})}
\end{align*}
